---
title: "Testing drake"
author: "Nathalia Graf-Grachet"
date: "1/5/2021"
output: html_document
---

I am following the directions from the `drake`'s [github repo](https://github.com/ropensci/drake).


## 1 - Load packages


```{r}
library(drake)
library(tidyverse)
```


## 2 - Custom function


```{r}
create_boxplot <- function(data, x_axis, y_axis, type_color) {
  ggplot(data) +
    geom_boxplot(aes(x = x_axis, y = y_axis, fill = type_color), show.legend = FALSE) +
    scale_fill_brewer(palette = "Set2") +
    theme_light(10)
}
```


## 3 - Make a plan


```{r}
analysis_plan <- drake_plan(
    PlantGrowth = read.csv("PlantGrowth.csv"),
    fig_boxplot = create_boxplot(PlantGrowth, PlantGrowth$group, PlantGrowth$weight, PlantGrowth$group)
)
```

```{r}
analysis_plan
```


The code above was just to set stage. 


## 4 - Let `drake` manage the analysis


```{r}
make(analysis_plan)
```


## 5 - Check the analysis


```{r}
readd(fig_boxplot)
```


## 6 - Make a modification


The original function to `create_boxplot()` is:
```
create_boxplot <- function(data, x_axis, y_axis, type_color) {
  ggplot(data) +
    geom_boxplot(aes(x = x_axis, y = y_axis, fill = type_color), show.legend = FALSE) +
    theme_light(10)
}
```

I want to go alter the color palette. So, I can go back to that code and add the palette I want like so (re-run the function):

```
create_boxplot <- function(data, x_axis, y_axis, type_color) {
  ggplot(data) +
    geom_boxplot(aes(x = x_axis, y = y_axis, fill = type_color), show.legend = FALSE) +
    scale_fill_brewer(palette = "Set2") +
    theme_light(10)
}
```


## 7 - Check `drake` provenance


Before re-running everything, check `drake`'s provenance:


```{r}
config = drake_config(analysis_plan)
vis_drake_graph(analysis_plan)
```


It will show what's outdated. In this case, `fig_boxplot` is outdated. To update the `analysis_plan`:


```{r}
make(analysis_plan)
```


Check the boxplot:


```{r}
readd(fig_boxplot)
```


Good. What about the `analysis_plan`?


```{r}
vis_drake_graph(analysis_plan)
```


Updated!